### 2018-06-15 Thesis/Parts/Data/Data.tex
data initial
data update

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Data}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Data}
The dataset we used for this research consists of all articles\footnote{From Elseviers corpus} published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals.

\begin{tabular}{c c c}
 & Total token count & Unique token count \\
Title & $14.742.192$ & $230.805$ \\
Abstract & $171.474.473$ & $738.961$ \\
Total & $186.962.354$ & $763.475$ \\
\end{tabular}
\end{document}

% RAW DATA:
% 1,391,543 articles
% 14 811 433 title tokens			230805 unique
% 172 150 921 abstract tokens		738961 unique
% 186 962 354 total tokens			763475 unique
% 3,759 journals

% split = 79.9509609117 - 20.0490390883

% training numbers
% 10K = percentage?}
